### 2020-02-02 article.tex
some conclusions added to sarraf method

Without a doubt, fMRI scans are nothing but spatial and temporal connectivities. As we aim to focus on spatial relations and put temporal ones aside, our algorithm must try to keep all of that information in calculations. Besides, Sarraf and Tofighi's method loses a lot of these connectivities by flattening data toward the $z$ axis. In addition to that, the mentioned data conversion will increase the model complexity and variance, especially in a case like Parkinson's disease dataset. In fact, by resizing 198 slices of $39 \times 64 \times 64$ voxels to a 2D $2496 \times 12672$ pixels, we are adding a lot of unnecessarily and incorrect spatial connectivities based on the $t$ axis and losing some important ones in the $z$ axis by misplacing them. As a result, it is predictable that flattening algorithm may lead to overfitting and compute-intensive calculations which can be seen in Figure \ref{fig:SarrafParkinsonTestResult}. This experiment ran on an NVIDIA\textsuperscript{\tiny\textregistered} GTX1080 and took $6h \; 47m \; 36s$.

>>>>

Without a doubt, fMRI scans are nothing but spatial and temporal connectivities. As we aim to focus on spatial relations and put temporal ones aside, our algorithm must try to keep all of that information in calculations. Besides, Sarraf and Tofighi's method loses a lot of these connectivities by flattening data toward the $z$ axis. In addition to that, the mentioned data conversion will increase the model complexity and variance, especially in a case like Parkinson's disease dataset. In fact, by resizing 198 slices of $39 \times 64 \times 64$ voxels to a 2D $2496 \times 12672$ pixels, we are adding a lot of unnecessarily and incorrect spatial connectivities based on the $t$ axis and losing some important ones in the $z$ axis by misplacing them. As a result, it is predictable that flattening algorithm may lead to overfitting and compute-intensive calculations which can be seen in Figure \ref{fig:SarrafParkinsonTestResult}. This experiment ran for 5 epochs (same as the article itself) on an NVIDIA\textsuperscript{\tiny\textregistered} GTX1080 and took $33h \; 55m \; 36s$ \tiny{($=6h \; 47m \; 7s$ for each epoch)}. From this experiment, we can easily observe the overfitting as the validation accuracy goes up and down alternatively, and the network is not able to improve the accuracy. Additionally, if we take a look at the loss diagram, we will find out that after the first epoch (which is highlighted by dots in the diagrams), no sensible change is happening to both parameters. Also, it worth mentioning that the model is trying to escape the regional optimum by increasing the loss of the training data while it faces no success.
